Parsing Postfix log files

### 2009-03-13 doc/logparser-implementation.tex
Removed some unused references.
Improved introduction and flow chart diagram in the flow chart section of the implementation chapter.

XXX FIGURE OUT WHEN TO USE ACTIONS AND WHEN TO USE ALGORITHM, PARSER,
ETC\@.

@@

From the viewpoint of an individual mail passing through the parser the
experience could be summarised as:

    \item Mail enters the system via \acronym{SMTP} or local submission.

    \item If the mail is rejected, save all data to the database and
        delete the connection entry from the state table.

    \item Follow the progress of the accepted mail until it is either
        delivered, bounced, or deleted, then save all data to the database,
        and delete the mail's entry from the state table.

\Figureref{flow chart image} shows the most common paths the data
representing a mail can take through the parser; the complications
described in \sectionref{complications} are excluded for the sake of
clarity.

@@

\label{mail enters the system}

Everything starts off with a mail entering the system, whether by local
submission via \daemon{postdrop}, by \acronym{SMTP}, by re-injection due to
forwarding, or internally generated by Postfix.  Local submission is the
simplest case: a queueid is assigned immediately and the sender address is
logged \flowchart{PICKUP}{2}.  Re-injection due to forwarding sadly lacks
explicit log lines of its own; it is explained in \sectionref{Re-injected
mails}.  Internally generated mails lack any explicit origin in Postfix
2.2.x and must be detected using heuristics as described in
\sectionref{identifying bounce notifications}.  Bounce notifications are
the primary example of internally generated mails, though there may be
other types.  Postfix may generate mails to the administrator when it
encounters configuration errors, but such mails are presumably rare.

@@

    \item This is followed by rejection of sender address, recipient
        addresses, client \acronym{IP} address or hostname, HELO hostname,
        etc.\ \flowchart{REJECTION}{4}; acceptance of one or more mails
        \flowchart{CLONE}{5}; or some interleaving of both.

>>>>

@@

A picture is said to be worth a thousand words: the flow chart in
\figureref{flow chart image} shows the most common paths a connection or
mail can take through \parsername{}; the parsing complications described in
\sectionref{complications} are excluded for the sake of clarity.

@@

Everything starts off with a mail entering the system, whether by local
submission via \daemon{postdrop}, by \acronym{SMTP}, by re-injection due to
forwarding, or internally generated by Postfix.  Local submission is the
simplest case: a queueid is assigned immediately and the sender address is
logged \flowchart{PICKUP}{2}.  Re-injection due to forwarding sadly lacks
explicit log lines of its own; it is explained fully in
\sectionref{Re-injected mails}.  Internally generated mails lack any
explicit origin in Postfix 2.2.x and must be detected using heuristics as
described in \sectionref{identifying bounce notifications}; later versions
of Postfix do provide log lines for internally generated mails.    Bounce
notifications are the primary example of internally generated mails, though
there are other types, e.g.\ Postfix may generate mails to the
administrator when it encounters configuration errors, but such mails are
presumably rare.

@@

    \item This is followed by rejection of sender address, recipient
        addresses, client \acronym{IP} address or hostname, HELO hostname,
        etc.\ \flowchart{DELIVERY\_REJECTED}{4}; acceptance of one or more
        mails \flowchart{CLONE}{5}; or some interleaving of both.
